Uncertainty Literature Review

### 2023-12-19 index.qmd
added in some bits for context section

## 2.1 The role of context in defining uncertainty
- (no visual distinction between sample/pop variance) @Bella2005 found that most participants were ignorant to the fact that error bars are used for both confidence intervals and standard error bars, two wildly different indicators of precision. (**also the paper sherry sent me**)
- **notes from the Xiao-li Meng papers**
- **papers that talk about task specific stuff**

>>>>

## 2.1 The role of context in defining uncertainty
When statistics is, at its core, the study of uncertainty, discussing uncertainty visualisation as though it is separate from other statistical visualisations is inherrently confusing. This distinction is largely ignored rather than clarified in the literature, and it leads to adjacent unanswered questions. Is our goal in uncertainty communication to acknowledge and convey the inherrent randomness that exists in all statistical calculations and models? Is it to supress signal that could be the result of random variance? Is it to find the best way to convey the mass function of a random variable? A survey of the literature will leave the answers to these questions unclear, however this inherrent issue has not gone unnoticed.

**need for task based understanding**
- several review papers acknowledge this issue is causing 
- **papers that talk about task specific stuff**
- This problem of a task based philosiphy extends all the way back to philisophical uncerstandings of statistics and variance.
- **notes from the Xiao-li Meng papers**
- **notes from john paper**
- While the statistics side brings up the purpose of a model or estimate for a philisophical consideration, it is a real, practical, and urgent problem for uncertainty visualisation. 
- **go through papers with endless different goals**
- **review paper that has an entire paragraph discussing differnet findings for box plots based on the task**

**need for statistics links**
- (no visual distinction between sample/pop variance) @Bella2005 found that most participants were ignorant to the fact that error bars are used for both confidence intervals and standard error bars, two wildly different indicators of precision. (**also the paper sherry sent me**)
